Spin canonical rings of log stacky curves

### 2015-07-10 surfaces-write-up/surface-write-up.tex
include g \geq 4 phrasing
don't know what changes are made?
surfaces: add theorem statement for one pt

\ssec{Notation}

Write
\begin{align*}
	D = \sum_{i=1}^{n}\alpha_i D_i.
\end{align*}
where $\alpha_i \in \bq.$

@@

Write
\begin{align*}
	D = \sum_{i=0}^{n}\alpha_i D_i.
\end{align*}
where $\alpha_i \in \bq$ and $\deg D_i = d_i$. Let $f_i$ be cartier divisors such that $D_i = V(f_i)$. We shall further assume that among there exist functions $f_0,\ldots, f_{m+1}$ form a basis for degree one rational functions on $\bp^m$.

@@

\ssec{One point on Projective Space}

@@

Notice that if $\gamma \in (R_D)_d$, then 
\[
	g = \sum_{i=1}^m {f_i}^{a_i}
\]
where each $a_i \ge - \alpha_i d_i$, $\sum_{i=1}^m a_i d_i = 0$, and $\sum_{i=1}^m a_i d_i' = 0$.  Then we can view $g$ inside of the lattice
$S\subseteq \mathbb{R}^{n+1}$ given by ordered elements of the form $(d, a_1, \ldots, a_n)$ satisfying $a_i \ge - d \alpha_i$ for all $i$, $\sum_{i=1}^m a_i d_i = 0$, and $\sum_{i=1}^m a_i d_i' = 0$. 
From here, determining a spanning set for $(R_D)_d$ reduces to finding the extremal rays of $S$ \todo{cite previous lemma}.

@@

For $i \in \{1, \ldots, m\}$ satisfying 
\begin{equation}\label{eqn:condition-for-e_i}
	d_i \sum_{l=1}^m d_l' \alpha_l = d_i' \sum_{l=1}^m d_l \alpha_l,
\end{equation}
define
\[
	\epsilon_i := (\prod_{l=1}^m f_l^{-\alpha l_i d_i}) (f_i^{\ell_i \sum_{l=1}^m \alpha_l d_l}) \in H^0(\ell_i d_i D).
\]
\todo{Peter: This equation above is very asymmetric in $d_i$ and $d_i'$.  Can we replace this with something in degree $\gcd(d_i, d_i')$? Otherwise, maybe its wrong and no such element actually exists in that degree (I think it exists, but will check again later to be sure)?}
For $i, j \in \{1, \ldots, m\}$ satisfying
\begin{equation}\label{eqn:condition-e_i,j-i}
	d_i \sum_{l=1}^m \alpha_l d_l' > d_i' \sum_{l=1}^m \alpha_i d_l
\end{equation}
and
\begin{equation}\label{eqn:condition-e_i,j-j}
	d_j \sum_{l=1}^m \alpha_l d_l' < d_j' \sum_{l=1}^m \alpha_j d_l
\end{equation}
then define
\[
	\epsilon_{i, j} = (\prod_{l=1}^m f_l^{-\alpha \ell_{i,j} (d_i d_j' - d_j d_i')}) {f_i}^{s_1} {f_j}^{s_2} \in H^0(l_{i,j}(d_i d_j' - d_j d_i')\ell_{i,j}D)
\]
where
\[
	s_1 = d_j' \sum_{l \ne i,j} \alpha_l d_l - d_j \sum_{l\ne i, j} \alpha_l d_l'
\]
and
\[
	s_2 = d_i' \sum_{l \ne i,j} \alpha_l d_l - d_i \sum_{l\ne i, j} \alpha_l d_l'.
\]
Let $E$ be the set of $\epsilon_i$ and $\epsilon_{i,j}$ given above, satisfying the respective conditions.
$E$ satisfies the conditions of proposition \todo{cite earlier proposition}, so by applying that proposition $R_D$ is generated in degree at most \todo{insert number}.
\end{proof}

@@

We are grateful to David Zureick-Brown for introducing us to the
study of stacky canonical rings, for providing invaluable guidance,
and for his mentorship. We also thank Ken Ono and the
Emory University Number Theory REU for arranging our project and
providing a great environment for mathematical learning and
collaboration.
Finally, we gratefully acknowledge the financial support given by
NSF Grant Award Number 1250467 via the Emory University Number
Theory REU. We deeply appreciate all of the support that has made
our work possible.

>>>>

\ssec{Notation}
\begin{convention}
Write
\begin{align*}
	D = \sum_{i=1}^{n}\alpha_i D_i.
\end{align*}
where $\alpha_i \in \bq$.
\end{convention}

\begin{convention}
Let $\{x_0, \ldots, x_m\}$ be coordinates for $\bp^m$. Let
$\vec{v} = (v_0, \ldots, v_m) \in \br^{m + 1}$. Then write
\[
	x_{\vec{v}} := \prod_{i = 0}^{m} x_i^{v_i}
\]
\end{convention}

@@

Write
\begin{align*}
	D = \sum_{i=0}^{n}\alpha_i D_i.
\end{align*}
where $\alpha_i \in \bq$ and $\deg D_i = d_i$. Let $f_i$ be Cartier divisors such that $D_i = V(f_i)$. We shall further assume that among there exist functions $f_0,\ldots, f_{m+1}$ form a basis for degree one rational functions on $\bp^m$.

@@

\begin{rem}
Remark about how we can assume divisor only consists of hyperplanes
by taking the Veronese embedding.
\end{rem}

\ssec{One point on Projective Space}
\label{ssec:proj-one-point}

\begin{thm}
\label{thm:proj-one-point}
Let $X = \bp^m$ with $\{x_0, \ldots, x_m\}$ a coordinate system for
$\bp^m$. Let $D = \frac{a}{b} H$, with $a, b \in \bz$ and $H =
V(x_k)$ a hyperplane of $\bp^m$, be a divisor on $\bp^m$. Let
\[
	\left\lfloor \frac{a}{b} \right\rfloor = \frac{c_0}{d_0} < \frac{c_1}{d_1} <
	\ldots < \frac{c_r}{d_r} = \frac{a}{b}
\]

\noindent
be the best lower approximations of $\frac{a}{b}$. Then the
canonical ring
\[
	R_D := \bigoplus_{d \geq 0} H^0(\bp^m, \lfloor dD \rfloor)
\]

\noindent
has a minimal presentation consisting of the $\sum_{i = 0}^{r}
{{m + i} \choose {i}}$ generators $\frac{u^d x_{\vec{v}}}{x_k^{c_i}}$
where $\vec{v} \in \bz_{\geq 0}^{m + 1}$ such that $\sum_{j = 0}^{m}
v_j = c_i$ and $z$ relations of the form
\[
	x_{\vec{u}} x_{\vec{v}} = x_{\vec{w}} x_{\vec{z}}
\]

\noindent
when $\sum_{i = 0}^{m + 1} u_i + v_i = \sum_{i = 0}^{m + 1} w_i + z_i$
\todo{fix this condition to make it right}
or of the form

\[
	x_{\vec{u}} x_{\vec{v}} = x_{\vec{w}} x_{\vec{z}}
\]

\noindent
when $\vec{u} + \vec{v} = \vec{w} + \vec{z}$.
\end{thm}

\begin{proof}

\end{proof}

@@

Notice that if $\gamma \in (R_D)_d$, then 
\[
	g = \sum_{i=1}^m {f_i}^{a_i}
\]
where each $a_i \ge - \alpha_i d_i$, $\sum_{i=1}^m a_i d = 0$, and $\sum_{i=1}^m a_i d_i' = 0$.  Then we can view $g$ inside of the lattice
$S\subseteq \mathbb{R}^{n+1}$ given by ordered elements of the form $(d, a_1, \ldots, a_n)$ satisfying $a_i \ge - d \alpha_i$ for all $i$, $\sum_{i=1}^m a_i d_i = 0$, and $\sum_{i=1}^m a_i d_i' = 0$. 
From here, determining a spanning set for $(R_D)_d$ reduces to finding the extremal rays of $S$ \todo{cite previous lemma}.

@@

For $i \in \{1, \ldots, m\}$ satisfying 
\begin{equation}\label{eqn:condition-for-e_i}
	d_i \sum_{l=1}^m d_l' \alpha_l = d_i' \sum_{l=1}^m d_l \alpha_l,
\end{equation}
define
\[
	\epsilon_i := (\prod_{l \ne i} f_l^{-\alpha l_i \gcd(d_i, d_i')}) (f_i^{\ell_i \frac{\gcd(d_i, d_i')}{d_i + d_i'}\sum_{l \ne i} \alpha_l (d_l + d_l')}) \in H^0(\ell_i \gcd(d_i, d_i') D).
\]
\todo{Peter: This equation above is very asymmetric in $d_i$ and $d_i'$.  Can we replace this with something in degree $\gcd(d_i, d_i')$? Otherwise, maybe its wrong and no such element actually exists in that degree (I think it exists, but will check again later to be sure)?}
For $i, j \in \{1, \ldots, m\}$ satisfying
\begin{equation}\label{eqn:condition-e_i,j-i}
	d_i \sum_{l=1}^m \alpha_l d_l' > d_i' \sum_{l=1}^m \alpha_i d_l
\end{equation}
and
\begin{equation}\label{eqn:condition-e_i,j-j}
	d_j \sum_{l=1}^m \alpha_l d_l' < d_j' \sum_{l=1}^m \alpha_j d_l
\end{equation}
then define
\[
	\epsilon_{i, j} = (\prod_{l=1}^m f_l^{-\alpha \ell_{i,j} (d_i d_j' - d_j d_i')}) {f_i}^{s_1} {f_j}^{s_2} \in H^0(\ell_{i,j}(d_i d_j' - d_j d_i')D)
\]
where
\[
	s_1 = d_j' \sum_{l \ne i,j} \alpha_l d_l - d_j \sum_{l\ne i, j} \alpha_l d_l'
\]
and
\[
	s_2 = d_i' \sum_{l \ne i,j} \alpha_l d_l - d_i \sum_{l\ne i, j} \alpha_l d_l'.
\]
Let $E$ be the set of $\epsilon_i$ and $\epsilon_{i,j}$ given above, satisfying the respective conditions.
$E$ satisfies the conditions of proposition \todo{cite earlier proposition}, so by applying that proposition $R_D$ is generated in degree at most \todo{insert number}.
\end{proof}

@@

We are grateful to David Zureick-Brown for introducing us to this
subject, for providing invaluable guidance,
and for his mentorship. We also thank Ken Ono and the
Emory University Number Theory REU for arranging our project and
providing a great environment for mathematical learning and
collaboration.
Finally, we gratefully acknowledge the financial support given by
NSF Grant Award Number 1250467 via the Emory University Number
Theory REU. We deeply appreciate all of the support that has made
our work possible.
